### 2021-03-03 yfcc100m/paper/vldb2021/design.tex

VDMS API provides a mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The information associated to each visual object (image, video, etc) is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve this objects based on its properties.
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
retrieval time.
Users can, for instance, retrieve a resized version of an image,
or retrieve only a clip from a large video.
This is one of the main differentiation aspect when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model supports (tables, columns).
This is, a SQL query can retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc).

>>>>

VDMS API provides a mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The information associated to each visual object (image, video, etc) is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve these objects based on its properties.
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
retrieval time.
Users can, for instance, retrieve a resized version of an image,
or retrieve only a clip from a large video.
This is one of the main differentiating aspects when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model supports (tables, columns).
This is, a SQL query can retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc).
